\chapter{State of art}

	Work in grammar-based compression has been made with different approaches.
	The most common way was using straight line grammars (SLG). 

	As stated in \cite{Benz}, a \emph{SLG} is a grammar that generates exactly one sequence, 
	so it doesn't	contain loops nor ambiguities.

	The general idea is to look for a grammar that represents a sequence without losing 
	information. \\

	The way to do that is searching for subsequences in such sequence that
	could be replaced by a Non Terminal symbol. By doing so, we could reduce the size
	of the sequence, because if we have a repeated subsequences, we can just assign
	a symbol to it and write the symbol instead of it. \\

	Each time we make a replacement we start over looking for new subsequences in the new sequence to 
	replace. The iteration process continue until we cannot compress it anymore.\\

	For example, an SLG from the follow sequence \cite{Benz}:

	\begin{center}
		\emph{ttatatttctttctttcttttttttcctcagcctcagagt}
	\end{center}

	could be: \\


	\begin{center}
	$S \rightarrow N_3ataN_3N_2N_2N_2N_3N_3N_3N_1N_1agt$\\
	$N_1 \rightarrow cctcag$ \\
	$N_2 \rightarrow tcN_3$ \\
	$N_3 \rightarrow tt$
	\end{center}


% \cite{GThesis}. \\

	When using this kind of grammars, the search of constituents to be replaced by non Terminals
	is commonly based on different types of repeats. Those could be Repeats, Maximal Repeats, Longest Maximal 
	Repeats, etc.
	Explanation about different repeats and its taxonomy can be founded here: \cite[p.42-46]{GThesis}.\\

	In the example given above those constituents obtainded from repeats in the sequence are $cctcag$, $tcN_3$, $tt$. \\

	But this approach has a limitation: what happend if there are words $w_1$..$w_n$ similar (with just some characters changed) to a repeat $R_i$ choosen as constituent? We would ignore them but they could be useful. 
	If we only use repeats, we could skip constituents of interest. \\

	For example, if we have the next sequence S:\\

	$S \rightarrow R_i\ --- R_i\ ---\ w_1\ w_2\ --- w_3\ ---\ ...\ ---\ R_i\ ---\ w_n\ $ \\

	Using the classical approach we would replace only the $R_i$: \\

	$S \rightarrow N\ ---\ N\ ---\ w_1\ w_2\ ---\ w_3\ ---\ ...\ ---\ N\ ---\ w_n\ $ \\

	But if we add some new rule N with ambiguity we could also replace the similar words $w_1, .. ,w_n$: \\

	$S \rightarrow N\ ---\ N\ ---\ N\ N\ ---\ N\ ---\ ...\ ---\ N\ --- N\ $ \\


	Based on this question, we started our work.
	In the next section we propose a way to be more flexible and to find interesting
	structural information.